Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-24 paper/snakemajoranas.tex
Split sentence explaining long flight times in two

\comment{The gap is small because of long trajectories.}
One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap~\cite{ren_topological_2018}; where the gap in the density of states significantly reduces for states with the momentum directed along the length of the strip.
From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
Additionally, these long trajectories have long flight times $\tau_f \approx D / v_F$ (see Fig.~\ref{fig:setup}), where $D$ is the length of the trajectory, and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.
This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, so a low filling of the bands is a workaround\cite{nijholt2015orbital}.
However, low filling requires precise knowledge of the system and might be more sensitive to disorder or microscopic inhomogeneities.
On the other hand, disorder scatters these long trajectories and introduces a cut-off on the scale of the mean-free path~\cite{haim_double-edge_2018}, however, disorder is impossible to control to a required precision experimentally.

>>>>

\comment{The gap is small because of long trajectories.}
One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap~\cite{ren_topological_2018}; where the gap in the density of states significantly reduces for states with the momentum directed along the length of the strip.
From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
Additionally, these long trajectories have long flight times $\tau_f \approx D / v_F$ (see Fig.~\ref{fig:setup}), with $D$ the trajectory length.
Equivalently, the Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$ are small, resulting in a small gap.
This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, so a low filling of the bands is a workaround\cite{nijholt2015orbital}.
However, low filling requires precise knowledge of the system and might be more sensitive to disorder or microscopic inhomogeneities.
On the other hand, disorder scatters these long trajectories and introduces a cut-off on the scale of the mean-free path~\cite{haim_double-edge_2018}, however, disorder is impossible to control to a required precision experimentally.
